The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2017-11-06 paper/ms.tex
Remove bold text

\begin{abstract}
We present the ``Galaxy Cluster Merger Catalog.'' This catalog provides an extensive suite of mock observations and related data for N-body and hydrodynamical simulations of galaxy cluster mergers {\bf and clusters from cosmological simulations}. These mock observations consist of projections of a number of important observable quantities in several different wavebands as well as along different lines of sight through each simulation domain. The web interface to the catalog consists of easily browseable images over epoch and projection direction, as well as download links for the raw data and a JS9 interface for interactive data exploration. {\bf The data is presented within a consistent format so that comparison between simulations is straightforward.} All of the data products are provided in the standard FITS file format. Data is being stored on the yt Hub~(\url{http://hub.yt}), which allows for remote access and analysis using a Jupyter notebook server. Future versions of the catalog will include simulations from a number of research groups and a variety of research topics related to the study of interactions of galaxy clusters with each other and with their member galaxies. The catalog is located at \url{http://gcmc.hub.yt}.
\end{abstract}

@@

We seek to address these issues by releasing the ``Galaxy Cluster Merger Catalog,'' an extensive suite of mock observations and related data for simulations of galaxy cluster mergers. We have produced 2D projections and slices of a number of different quantities relevant to observations of galaxy clusters {\bf from simulations of binary cluster mergers and cosmological simulations. {\bf These data products include clusters in various stages of merging and interaction with other systems viewed along a number of relevant projection axes. The data from the various simulations are presented within a consistent format so that comparison between simulations with different physics or different initial conditions is straightforward.} The inclusion of data from both simulation types emphasizes the strengths of each: idealized merger simulations, due to their typically higher resolution and controlled set up, can provide insights into what kind of physics and merger configurations lead to certain observable features in cluster mergers. On the other hand, cosmological simulations capture more realistic mergers between clusters with substructure as well as cosmological accretion, providing a more direct comparison with observations.}

The goal of this catalog is to provide a way to connect {\bf a variety of} simulations of galaxy cluster mergers {\bf within a common interface} with multiwavelength observations of real merging clusters, providing an opportunity for observers to compare clusters in their observations with a particular merging scenario. {\bf For example, the catalog may be used to interpret existing observations across multiple wavebands such as the Planck-Chandra Cluster Sample\footnote{\url{https://hea-www.harvard.edu/CHANDRA_PLANCK_CLUSTERS/}} \citep{jon16}, or be analyzed to make predictions for what various investigations of real clusters may reveal for future observations and missions, such as {\it Athena}\footnote{\url{http://www.the-athena-x-ray-observatory.eu/}} and {\it Lynx}\footnote{\url{https://wwwastro.msfc.nasa.gov/lynx/}}}.

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger simulations {\bf and one cosmological simulation}. {\bf The original works from which these simulations are drawn, in addition to some details of the simulations, are listed in Table \ref{tab:sim_table}.} The types of data products listed here are appropriate for such simulations. In the future, the catalog will include data products {\bf from additional simulations of idealized binary mergers, cosmological simulations, and simulations of interactions between clusters and their member galaxies.} The types of data products are likely to expand and diversify with the inclusion of new simulations. \textbf{For more discussion of future directions for the catalog and long-term issues, see Section \ref{sec:future}}.

@@

The galaxy cluster merger simulation data in the catalog comes from state-of-the-art N-body and hydrodynamics codes such as FLASH \citep{dub09}, {\bf ART \citep{kra99, kra02, rud08}}, and Athena \citep{sto08}. The exact physics and algorithms employed by the simulations vary, but in general:

\begin{itemize}
\item Each simulation is simulated using an adaptive or static mesh refinement (AMR/SMR) grid \citep{ber89} with varying resolution throughout the domain, with refinement occuring on criteria such as sharp jumps in density and temperature, matter density, and selected regions such as the cluster center.
\item The equations of hydrodynamics (HD) or magnetohydrodynamics (MHD) are modeled using a conservative finite-volume scheme, employing Riemann solvers for evolving the flux of physical quantities and using high-order reconstruction schemes such as the Piecewise-Parabolic Method \citep[PPM,][]{col84}. If present, magnetic fields are evolved such that the condition $\nabla \cdot {\bf B} = 0$ is met, typically by a constrained transport scheme \citep[CT,][]{eva88}.
\item Each simulation assumes an ideal gas law equation of state with $\gamma = 5/3$ and primordial abundances of H/He with trace amounts of metals, yielding a mean molecular weight of $\mu \simeq 0.6$.
\item If dark matter is included, it is modeled by an N-body solver for a collection of collisionless massive particles, which interact with the gas component only via gravity.
\item The gravity in the simulations is either modeled as a rigid gravitational potential associated with each cluster or by computing the self-gravity of the gas and dark matter using a Poisson solver \citep[e.g.,][]{ric08}.
\item {\bf Cosmological simulations in the catalog include the effect of cosmological expansion by evolving the equations of hydrodynamics and particle advancement in comoving coordinates and with terms including the dependence on the scale factor of the universe.}
\item Depending on the goals of the simulation study, other physics, such as viscosity, thermal conduction, radiative cooling, star formation and energy feedback from black holes, etc., may be included.
\end{itemize}

@@

The catalog data is stored on the \code{yt Hub}\footnote{\url{https://hub.yt/}}, a conglomerate of various open source
services \textbf{hosted at the National Center for Supercomputing Applications (NCSA)}, creating an environment that allows one to collect, remotely analyze, share and publish scientific datasets. At its core, the \code{yt Hub} uses \code{Girder}\footnote{\url{https://girder.readthedocs.io}}, a data management platform that allows to transparently store, serve, and proxy data from heterogeneous backend storage engines through a single
web API. Data served by \code{Girder} can easily be gathered into dynamical hierarchies such as collections, folders, and
items. This data management system is integrated with \code{JupyterHub}\footnote{\url{https://jupyterhub.readthedocs.io/}} and allows authenticated users to spawn Jupyter notebook servers with direct access to the data that is provided as a dynamically composed FUSE filesystem. Any Jupyter
notebook created in that environment during an interactive session is safely stored back in the \code{Girder} instance,
preserving the user's analysis workflow and increasing research reproducibility. In the future, we plan to have this
notebook capability integrated directly with the catalog website.

@@

The web interface to the catalog is designed to provide straightforward interactive browsing of a given simulation's data across its many epochs and between several projection axes. This facilitates comparisons between the mock observations and actual observations of clusters so that a potential analog of a particular system may be found easily. \textbf{Like the data itself, the web interface is also hosted at NCSA.}

The portion of the website containing the simulation data is structured using the a hierarchy of pages. {\bf Simulations are grouped together in ``sets'', which are simulations with shared characteristics. The page for each simulation within a set has links to pages for the different epochs (or individual cluster halos in the case of a cosmological simulation). Finally, the page for each epoch or halo within a simulation provides the access to the corresponding data products that were described above. We now describe these pages in detail.}

@@

{\bf The highest level of organization within the catalog is that of a ``set'' of simulations, which are simulations with shared characteristics. For example, these may be simulations with identical initial conditions but different input physics (e.g., pure hydrodynamics versus MHD, or a non-radiative cosmological simulation versus a simulation with star formation and feedback), or simulations with identical physics but different initial conditions (e.g., varying the mass ratio and/or impact parameter in binary merger simulations). Simulations within a set were run with the same code.} The ``set page'' describes the general characteristics of a single set of simulations from a particular investigation and provides links to the {\bf data for the} individual simulations. This page also provides links to journal articles which the simulation data appeared in, as well as basic characteristics of the simulation data including the size of the domain, the finest cell size, the characteristic mass of the clusters, {\bf the cosmological parameters,} etc. This page may also include links to supplementary data files that are common to all of the simulations in the set.

@@

Every simulation of a set has a ``simulation page'' which shows various quantities projected perpendicular to the merger plane for every epoch {\bf or halo} of the simulation that is available. The different epochs {\bf or halos} can be navigated using a slider bar, and buttons above the slider bar can be used to look at the same images from a different line of sight. The links attached to the images lead to the epoch {\bf or halo} pages {\bf for this simulation}.

@@

Any given link on the simulation page leads to an ``epoch page'' or ``halo page'' where images from a particular simulation epoch {\bf for idealized simulations, or a particular halo for cosmological simulations,} can be examined and the corresponding data may be obtained. Links are provided to similar simulations with different input physics at the same epoch {\bf or for the same halo}. This page also contains information about the different types of data within the files. A drop-down menu is provided for switching between the different projection axes available.

A link is provided on each epoch {\bf or halo} page to the location of the files on the \code{yt Hub}, so that one may start Jupyter notebooks with access to the data. Each epoch page also contains a JS9 application for opening the various FITS files associated with that particular epoch {\bf or halo}. A drop-down menu is provided for navigating between the various fields in each FITS file.

@@

{\bf There are a number of extensions to the catalog and its capabilities that we envision for the future, which we briefly discuss in this section.}

@@

{\bf The catalog is designed to be easily expanded to include new simulation data products related to galaxy cluster mergers or the more general arena of galaxy clusters, groups, or galaxies in the cosmological context. One way to encourage the inclusion of new simulations in the catalog is to provide Python scripts which may be used to generate the data products, including FITS image and table files and PNG images. A future version of the catalog will include a suite of such scripts which will be publicly available for this purpose, and directions for how to upload the resultant products to the \code{yt Hub}.}

@@

{\bf The current data products include slices and projections of various physical quantities, but they have a distinct tilt towards X-ray observations of clusters due to the focus of the simulations included so far on the physics of the ICM. Many other simulations of clusters available in the literature have additional physics included in the simulation, such as star formation, active galactic nuclei, and relativistic particle acceleration. These physical processes produce observations in other wavebands, such as the optical, ultraviolet, or radio, which could be included as simulated observations in the form of new FITS image or table types in the catalog.}

@@

{\bf Maintaining such a large catalog of data, whether from simulations or otherwise, is a substantial undertaking. It first and foremost requires that the computational resources necessary to store the data and serve it to users will be maintained and funded for the forseeable future. The website \url{http://gcmc.hub.yt} itself (including the widgets, documentation, and user interface) is completely separated from the data itself, which is hosted on the yt Hub. Therefore it is completely portable, and may be hosted virtually anywhere, provided proper configuration of Cross-Origin Resource Sharing (CORS) between it and the \code{yt Hub}.

@@

The second important resource is of course that of the human beings who are maintaining and updating the catalog. The authors themselves are committed to the long-term development and maintenance of the various components required to sustain this project, and our hope is that by getting more researches involved by including their data we can make the catalog a project which is sustained by a wider community. As a first step toward this goal, the code for the website is open-source and hosted at \url{http://github.com/jzuhone/cluster_merger_catalog}. Next steps include streamlining the code for the website itself and providing templates to simplify the generation of pages for new simulations, including directions for how to create a new set of pages for a simulation and how to submit them as a pull request to the repository.}

@@

We {\bf have presented} the ``Galaxy Cluster Merger Catalog,'' a website designed to provide a simple yet powerful interface to accessing mock observations of {\bf galaxy clusters}. {\bf The catalog} includes a suite of mock observations from a number of binary cluster merger {\bf and cosmological} simulations, with different initial conditions and/or input physics. In particular, the catalog provides a number of X-ray and S-Z synthetic observations as well as mock galaxy catalogs {\bf for some simulations}. Projections of the observables have been taken along a number of lines of sight through the simulation box, and at a large number of epochs for each simulation so that the merger history is well-sampled in time. {\bf The catalog interface is designed to facilitate quick and straightforward comparisons between the different simulations.} This large parameter space of cluster mergers will be useful when comparing with observed cluster mergers in a number of wavebands.

@@

\textbf{At the time of writing, the catalog includes data products from binary merger simulations carried out by the first author, and from a cosmological simulation carried out by \citet{nel14}. The catalog is released and designed with the intent that it may be expanded to include simulation data products related to galaxy cluster mergers or the broader subject of cosmological structure formation from other works and authors. We have already received a positive response from the community in this regard and have plans underway to incorporate new simulations into the catalog in the near future.}

{\bf Comparisons of data from the catalog to current observations have already been made to useful effect by \citet{wal17} and Douglass et al. 2017, in preparation. The catalog is also being explored as an avenue for further simulation investigations as well. The simulated X-ray images from several of the simulations are currently being analyzed with edge-detection techniques to determine if such an approach can reveal differences in the X-ray surface brightness distribution produced by varying the plasma physics of the ICM, including the strength of the magnetic field and viscosity (Bellomi et al., in preparation). Another area of research that is being explored by the authors of this work involves extracting cluster merger parameters from mergers in cosmological simulations and using them as inputs for idealized simulations, applying different prescriptions for the physics of the ICM in different simulations. This will be particularly useful from the perspective of determining the effect of varying the ICM physics on the velocity field of merging clusters, which will be an area of intense research with the advent of X-ray observatories carrying instruments which can measure such motions. The fruits of this research will eventually become part of the catalog as well.} It is our hope that the catalog will {\bf continue to provide} a useful resource for researchers studying galaxy cluster mergers from both the perspective of current observations as well as making predictions for future missions.

>>>>

\begin{abstract}
We present the ``Galaxy Cluster Merger Catalog.'' This catalog provides an extensive suite of mock observations and related data for N-body and hydrodynamical simulations of galaxy cluster mergers and clusters from cosmological simulations. These mock observations consist of projections of a number of important observable quantities in several different wavebands as well as along different lines of sight through each simulation domain. The web interface to the catalog consists of easily browseable images over epoch and projection direction, as well as download links for the raw data and a JS9 interface for interactive data exploration. The data is presented within a consistent format so that comparison between simulations is straightforward. All of the data products are provided in the standard FITS file format. Data is being stored on the yt Hub~(\url{http://hub.yt}), which allows for remote access and analysis using a Jupyter notebook server. Future versions of the catalog will include simulations from a number of research groups and a variety of research topics related to the study of interactions of galaxy clusters with each other and with their member galaxies. The catalog is located at \url{http://gcmc.hub.yt}.
\end{abstract}

@@

We seek to address these issues by releasing the ``Galaxy Cluster Merger Catalog,'' an extensive suite of mock observations and related data for simulations of galaxy cluster mergers. We have produced 2D projections and slices of a number of different quantities relevant to observations of galaxy clusters from simulations of binary cluster mergers and cosmological simulations. These data products include clusters in various stages of merging and interaction with other systems viewed along a number of relevant projection axes. The data from the various simulations are presented within a consistent format so that comparison between simulations with different physics or different initial conditions is straightforward. The inclusion of data from both simulation types emphasizes the strengths of each: idealized merger simulations, due to their typically higher resolution and controlled set up, can provide insights into what kind of physics and merger configurations lead to certain observable features in cluster mergers. On the other hand, cosmological simulations capture more realistic mergers between clusters with substructure as well as cosmological accretion, providing a more direct comparison with observations.

The goal of this catalog is to provide a way to connect a variety of simulations of galaxy cluster mergers within a common interface with multiwavelength observations of real merging clusters, providing an opportunity for observers to compare clusters in their observations with a particular merging scenario. For example, the catalog may be used to interpret existing observations across multiple wavebands such as the Planck-Chandra Cluster Sample\footnote{\url{https://hea-www.harvard.edu/CHANDRA_PLANCK_CLUSTERS/}} \citep{jon16}, or be analyzed to make predictions for what various investigations of real clusters may reveal for future observations and missions, such as {\it Athena}\footnote{\url{http://www.the-athena-x-ray-observatory.eu/}} and {\it Lynx}\footnote{\url{https://wwwastro.msfc.nasa.gov/lynx/}}.

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger simulations and one cosmological simulation. The original works from which these simulations are drawn, in addition to some details of the simulations, are listed in Table \ref{tab:sim_table}. The types of data products listed here are appropriate for such simulations. In the future, the catalog will include data products from additional simulations of idealized binary mergers, cosmological simulations, and simulations of interactions between clusters and their member galaxies. The types of data products are likely to expand and diversify with the inclusion of new simulations. For more discussion of future directions for the catalog and long-term issues, see Section \ref{sec:future}.

@@

The galaxy cluster merger simulation data in the catalog comes from state-of-the-art N-body and hydrodynamics codes such as FLASH \citep{dub09}, ART \citep{kra99, kra02, rud08}, and Athena \citep{sto08}. The exact physics and algorithms employed by the simulations vary, but in general:

\begin{itemize}
\item Each simulation is simulated using an adaptive or static mesh refinement (AMR/SMR) grid \citep{ber89} with varying resolution throughout the domain, with refinement occuring on criteria such as sharp jumps in density and temperature, matter density, and selected regions such as the cluster center.
\item The equations of hydrodynamics (HD) or magnetohydrodynamics (MHD) are modeled using a conservative finite-volume scheme, employing Riemann solvers for evolving the flux of physical quantities and using high-order reconstruction schemes such as the Piecewise-Parabolic Method \citep[PPM,][]{col84}. If present, magnetic fields are evolved such that the condition $\nabla \cdot {\bf B} = 0$ is met, typically by a constrained transport scheme \citep[CT,][]{eva88}.
\item Each simulation assumes an ideal gas law equation of state with $\gamma = 5/3$ and primordial abundances of H/He with trace amounts of metals, yielding a mean molecular weight of $\mu \simeq 0.6$.
\item If dark matter is included, it is modeled by an N-body solver for a collection of collisionless massive particles, which interact with the gas component only via gravity.
\item The gravity in the simulations is either modeled as a rigid gravitational potential associated with each cluster or by computing the self-gravity of the gas and dark matter using a Poisson solver \citep[e.g.,][]{ric08}.
\item Cosmological simulations in the catalog include the effect of cosmological expansion by evolving the equations of hydrodynamics and particle advancement in comoving coordinates and with terms including the dependence on the scale factor of the universe.
\item Depending on the goals of the simulation study, other physics, such as viscosity, thermal conduction, radiative cooling, star formation and energy feedback from black holes, etc., may be included.
\end{itemize}

@@

The catalog data is stored on the \code{yt Hub}\footnote{\url{https://hub.yt/}}, a conglomerate of various open source
services hosted at the National Center for Supercomputing Applications (NCSA), creating an environment that allows one to collect, remotely analyze, share and publish scientific datasets. At its core, the \code{yt Hub} uses \code{Girder}\footnote{\url{https://girder.readthedocs.io}}, a data management platform that allows to transparently store, serve, and proxy data from heterogeneous backend storage engines through a single
web API. Data served by \code{Girder} can easily be gathered into dynamical hierarchies such as collections, folders, and
items. This data management system is integrated with \code{JupyterHub}\footnote{\url{https://jupyterhub.readthedocs.io/}} and allows authenticated users to spawn Jupyter notebook servers with direct access to the data that is provided as a dynamically composed FUSE filesystem. Any Jupyter
notebook created in that environment during an interactive session is safely stored back in the \code{Girder} instance,
preserving the user's analysis workflow and increasing research reproducibility. In the future, we plan to have this
notebook capability integrated directly with the catalog website.

@@

The web interface to the catalog is designed to provide straightforward interactive browsing of a given simulation's data across its many epochs and between several projection axes. This facilitates comparisons between the mock observations and actual observations of clusters so that a potential analog of a particular system may be found easily. Like the data itself, the web interface is also hosted at NCSA.

The portion of the website containing the simulation data is structured using the a hierarchy of pages. Simulations are grouped together in ``sets'', which are simulations with shared characteristics. The page for each simulation within a set has links to pages for the different epochs (or individual cluster halos in the case of a cosmological simulation). Finally, the page for each epoch or halo within a simulation provides the access to the corresponding data products that were described above. We now describe these pages in detail.

@@

The highest level of organization within the catalog is that of a ``set'' of simulations, which are simulations with shared characteristics. For example, these may be simulations with identical initial conditions but different input physics (e.g., pure hydrodynamics versus MHD, or a non-radiative cosmological simulation versus a simulation with star formation and feedback), or simulations with identical physics but different initial conditions (e.g., varying the mass ratio and/or impact parameter in binary merger simulations). Simulations within a set were run with the same code. The ``set page'' describes the general characteristics of a single set of simulations from a particular investigation and provides links to the data for the individual simulations. This page also provides links to journal articles which the simulation data appeared in, as well as basic characteristics of the simulation data including the size of the domain, the finest cell size, the characteristic mass of the clusters, the cosmological parameters, etc. This page may also include links to supplementary data files that are common to all of the simulations in the set.

@@

Every simulation of a set has a ``simulation page'' which shows various quantities projected perpendicular to the merger plane for every epoch or halo of the simulation that is available. The different epochs or halos can be navigated using a slider bar, and buttons above the slider bar can be used to look at the same images from a different line of sight. The links attached to the images lead to the epoch or halo pages for this simulation.

@@

Any given link on the simulation page leads to an ``epoch page'' or ``halo page'' where images from a particular simulation epoch for idealized simulations, or a particular halo for cosmological simulations, can be examined and the corresponding data may be obtained. Links are provided to similar simulations with different input physics at the same epoch or for the same halo. This page also contains information about the different types of data within the files. A drop-down menu is provided for switching between the different projection axes available.

A link is provided on each epoch or halo page to the location of the files on the \code{yt Hub}, so that one may start Jupyter notebooks with access to the data. Each epoch page also contains a JS9 application for opening the various FITS files associated with that particular epoch or halo. A drop-down menu is provided for navigating between the various fields in each FITS file.

@@

There are a number of extensions to the catalog and its capabilities that we envision for the future, which we briefly discuss in this section.

@@

The catalog is designed to be easily expanded to include new simulation data products related to galaxy cluster mergers or the more general arena of galaxy clusters, groups, or galaxies in the cosmological context. One way to encourage the inclusion of new simulations in the catalog is to provide Python scripts which may be used to generate the data products, including FITS image and table files and PNG images. A future version of the catalog will include a suite of such scripts which will be publicly available for this purpose, and directions for how to upload the resultant products to the \code{yt Hub}.

@@

The current data products include slices and projections of various physical quantities, but they have a distinct tilt towards X-ray observations of clusters due to the focus of the simulations included so far on the physics of the ICM. Many other simulations of clusters available in the literature have additional physics included in the simulation, such as star formation, active galactic nuclei, and relativistic particle acceleration. These physical processes produce observations in other wavebands, such as the optical, ultraviolet, or radio, which could be included as simulated observations in the form of new FITS image or table types in the catalog.

@@

Maintaining such a large catalog of data, whether from simulations or otherwise, is a substantial undertaking. It first and foremost requires that the computational resources necessary to store the data and serve it to users will be maintained and funded for the forseeable future. The website \url{http://gcmc.hub.yt} itself (including the widgets, documentation, and user interface) is completely separated from the data itself, which is hosted on the yt Hub. Therefore it is completely portable, and may be hosted virtually anywhere, provided proper configuration of Cross-Origin Resource Sharing (CORS) between it and the \code{yt Hub}.

@@

The second important resource is of course that of the human beings who are maintaining and updating the catalog. The authors themselves are committed to the long-term development and maintenance of the various components required to sustain this project, and our hope is that by getting more researches involved by including their data we can make the catalog a project which is sustained by a wider community. As a first step toward this goal, the code for the website is open-source and hosted at \url{http://github.com/jzuhone/cluster_merger_catalog}. Next steps include streamlining the code for the website itself and providing templates to simplify the generation of pages for new simulations, including directions for how to create a new set of pages for a simulation and how to submit them as a pull request to the repository.

@@

We have presented the ``Galaxy Cluster Merger Catalog,'' a website designed to provide a simple yet powerful interface to accessing mock observations of galaxy clusters. The catalog includes a suite of mock observations from a number of binary cluster merger and cosmological simulations, with different initial conditions and/or input physics. In particular, the catalog provides a number of X-ray and S-Z synthetic observations as well as mock galaxy catalogs for some simulations. Projections of the observables have been taken along a number of lines of sight through the simulation box, and at a large number of epochs for each simulation so that the merger history is well-sampled in time. The catalog interface is designed to facilitate quick and straightforward comparisons between the different simulations. This large parameter space of cluster mergers will be useful when comparing with observed cluster mergers in a number of wavebands.

@@

At the time of writing, the catalog includes data products from binary merger simulations carried out by the first author, and from a cosmological simulation carried out by \citet{nel14}. The catalog is released and designed with the intent that it may be expanded to include simulation data products related to galaxy cluster mergers or the broader subject of cosmological structure formation from other works and authors. We have already received a positive response from the community in this regard and have plans underway to incorporate new simulations into the catalog in the near future.

Comparisons of data from the catalog to current observations have already been made to useful effect by \citet{wal17} and Douglass et al. 2017, in preparation. The catalog is also being explored as an avenue for further simulation investigations as well. The simulated X-ray images from several of the simulations are currently being analyzed with edge-detection techniques to determine if such an approach can reveal differences in the X-ray surface brightness distribution produced by varying the plasma physics of the ICM, including the strength of the magnetic field and viscosity (Bellomi et al., in preparation). Another area of research that is being explored by the authors of this work involves extracting cluster merger parameters from mergers in cosmological simulations and using them as inputs for idealized simulations, applying different prescriptions for the physics of the ICM in different simulations. This will be particularly useful from the perspective of determining the effect of varying the ICM physics on the velocity field of merging clusters, which will be an area of intense research with the advent of X-ray observatories carrying instruments which can measure such motions. The fruits of this research will eventually become part of the catalog as well. It is our hope that the catalog will continue to provide a useful resource for researchers studying galaxy cluster mergers from both the perspective of current observations as well as making predictions for future missions.
